Randomise papers

### 2024-07-28 Randomisation/Archive/Randomise_Papers.qmd

---
title: Randomise papers
subtitle: Describes random selection of papers for inclusion in the review
author: Saoirse Kelleher
date: today
format: 
  html:
    code-fold: true
    theme: minty
    toc: true
bibliography: references.bib
---

@@

```{r load packages}
#| message: false
library("knitr")
library("tidyverse") 
library("readxl")

>>>>

---
title: Randomise papers
subtitle: Describes random selection of papers for inclusion in the review
author: Saoirse Kelleher
date: today
format: 
  html:
    code-fold: true
    theme: minty
    toc: true
    embed-resources: true
bibliography: references.bib
---

@@

```{r load packages}
#| message: false

options(tidyverse.quiet = TRUE)
library("knitr")
library("tidyverse")
library("readxl")
